Analysis2

### 2023-11-10 Lahman Analysis/Rough Analysis 2/Analysis2.qmd
11/10 Meeting

@@

>>>>

### 11/10 Meeting

```{r}
N_player <- Batting %>% 
  distinct(playerID) %>% 
  pull(playerID) %>% 
  sample(size = 100, replace = FALSE)
```

```{r}
Samp_Batting <-  Batting %>% 
  filter(playerID %in% N_player)
```

```{r}
Samp_Batting <- Samp_Batting %>% 
  select(!park_index) %>% 
  mutate(park = as.character(park)) %>% 
  mutate(park = as.factor(park)) %>% 
  mutate(park_index = as.integer(park), .after = park) %>% 
  mutate(player_index = as.factor(playerID), .after = playerID) %>% 
  mutate(player_index = as.integer(player_index))
```

```{r}
data28aa <- list(
  N = nrow(Samp_Batting),
  n_player = n_distinct(Samp_Batting$player_index),
  AB = Samp_Batting %>% pull(AB),
  HR = Samp_Batting %>% pull(HR),
  Player = Samp_Batting %>% pull(player_index),
  cAge = Samp_Batting %>% pull(Age) -30
)
```

```{r}
fit28aa <- stan(
  file = "HR28aa.stan",
  data = data28aa,
  iter = 200
)
```

```{r}
plot(fit28aa, pars="beta0")
```

```{r}
plot(fit28aa, pars="beta1")
```

```{r}
data28ab <- list(
  N = nrow(Samp_Batting),
  n_player = n_distinct(Samp_Batting$player_index),
  AB = Samp_Batting %>% pull(AB),
  HR = Samp_Batting %>% pull(HR),
  Player = Samp_Batting %>% pull(player_index),
  cAge = Samp_Batting %>% pull(Age) -30,
  cAgeSq = (Samp_Batting %>% pull(Age) -30)**2
)
```

```{r}
fit28ab <- stan(
  file = "HR28ab.stan",
  data = data28ab,
  iter = 500
)
```

```{r}
plot(fit28ab, pars="beta0")
plot(fit28ab, pars = "beta1")
plot(fit28ab, pars = "beta2")
```

Start plotting individual player's home run "trajectories" to see how the model is doing. Should be a parabola from the means of the posterior. This would show the logit of player home runs. Prefer players who have lots of seasons to start and then do it for players who have very little seasons.

After, consider either more than 100 players or add in other effects like park effects.

@@

200 iterations took 15 minutes. So, we should wait until we have some time to render this or really try and get this to work on my PC.
